Kyoto VR MQP Paper First Draft

### 2019-09-26 paper.tex
fix more typos

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. This means a few different things. For starters, many AR
apps and features available on smartphones offer very little in the way of
functionality or practicality; quite simply, they are primarily used for minor
spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one
of the most popular apps to use AR, Pokemon GO, primarily uses it's AR feature
to place a Pokemon in the world aroudn you through your phone camera for you to
capture. But when it is in the world, it does not interact with anything around
it. It just floats a fixed distance away from you, simply placed on top of your
camera's video feed.

Additionally, in many cases where AR is used, the task could be accomplished as
well or better without AR~\autocite{theappsolutions2018}. Returning to the
Pokemon GO example, when the AR feature is left on while capturing a Pokemon,
the extra power needed for this feature drains the device faster, makes it
harder to hit the Pokemon with a Pokeball due to the model drifting in the
environment, and can even slow app performance, all of which detract from the
ability to play and enjoy the game.

@@

Wikitude is another major AR development kit that is very prevalent in the
world of AR development. It has over 130,000 registered AR developers, and is
powering over 30,000 AR apps across smartphones, tablets, and smart
glasses~\autocite{wikitude2018}.  And it's easy to understand why Wikitude has
so many registered developers when you see the list of features it offers. Some
of the features that appealed most to us were their Instant Tracking, allowing
for augmentation using flat surfaces; Image Tracking, allowing for augmentation
using one or multiple 2D images; and Geo AR, allowing for creation of geo
markers at specific locations to triggered AR content~\autocite{wikitude2018}.

@@

The company motive.io used to work on a product that would allow users to
create an engaging AR experience in the style of Pokemon Go. Their service
would have purportedly handled technical details such as hosting, storage, and
user accounts. The promotional video shows the creation of a location-based AR
game where the user pretends to hack into ATMs using the real-world locations
of ATMs in a city\autocite{odom2017}.

@@

In a question submitted to \textit{Compute!} magazine asking whether it is
possible for a Commodore 64 to emulate MS-DOS, the editor responded ``Yes, it's
possible for a 64 to emulate an IBM PC, in the same sense that it's possible to
bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
``Emulation is a complex business, but here's one rule of thumb: The only way to
successfully emulate a machine is with a much more powerful
machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
operating system is closer to emulating a C64 on an IBM PC running MS-DOS
(rather than the other way around, thankfully). The moral is that the speed
problem facing emulators is just as real as it was in 1988. Considering that AR
already pushes modern phone harware to the limit, emulation is not something is
not something we wanted to struggle with. On top of this, our testing required
us to move the camera through the world at various speeds and angles, which is
simply cumbersome with a laptop webcam.

@@

The goal of Editour is to allow a non-technical user to design audio tours
through a web-app. At its core, Editour is a tool to draw arbitarily-shaped
geographic regions onto a map.

@@

Even with knowledge of C\# and Unity, inputing tour data this way is obviously
not convenient. Atticus reminded us that, although he has a working knowledge
of Unity, he is not a software developer [citation needed for personal
communication.] In order to make our app prototype at all useful for the
future, we needed to provide an easy way to ``design'' a tour.

@@

\begin{minted}{json}
{
   "regions": [
      {
         "name": "Beautiful Place",
         "points": [ {"lat": 23.4, "lng": 56.7}, /* list omitted for brevity */ ],
         "audio": [ "beautiful-audio.mp3" ],
         "images": [ "mountain.jpg", "stream.jpg" ],
         "transcript": "To your left, you can see a beautiful place."
      },
      {
         "name": "Gorgeous Place",
         "points": [ {"lat": 12.3, "lng": 45.6}, /* list omitted for brevity */ ],
         "audio": [ "gorgeous-audio.mp3" ],
         "images": [ "hill.jpg", "valley.jpg", "gorge.jpg" ],
         "transcript", "To your right, you can see a gorgeous place."
      }
   ]
}
\end{minted}

@@

The backend implements a representational state transfer (REST) API, utilizing
HTTP methods to manipulate tour data on the server. For full documentation of
the backend's API, see Appendix~\ref{sec:editourAPIDocumentation}.

@@

Here is a list of API functions the Editour backend handles. The response is
usually a JSON like this with fields called \texttt{status} and \texttt{message}
The status is an HTTP status code like 200 (OK) or 404 (Not Found), and the
message is a string or stringified JSON that contains the data of the response.

>>>>

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. This means a few different things. For starters, many AR
apps and features available on smartphones offer very little in the way of
functionality or practicality; quite simply, they are primarily used for minor
spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one
of the most popular apps to use AR, Pokémon GO, primarily uses it's AR feature
to place a Pokémon in the world around you through your phone camera for you to
capture. But when it is in the world, it does not interact with anything around
it. It just floats a fixed distance away from you, simply placed on top of your
camera's video feed.

Additionally, in many cases where AR is used, the task could be accomplished as
well or better without AR~\autocite{theappsolutions2018}. Returning to the
Pokémon GO example, when the AR feature is left on while capturing a Pokémon,
the extra power needed for this feature drains the device faster, makes it
harder to hit the Pokémon with a Pokéball due to the model drifting in the
environment, and can even slow app performance, all of which detract from the
ability to play and enjoy the game.

@@

Wikitude is another major AR development kit that is very prevalent in the
world of AR development. It has over 130,000 registered AR developers, and is
powering over 30,000 AR apps across smartphones, tablets, and smart
glasses~\autocite{wikitude2018}.  And it's easy to understand why Wikitude has
so many registered developers when you see the list of features it offers. Some
of the features that appealed most to us were their Instant Tracking, allowing
for augmentation using flat surfaces; Image Tracking, allowing for augmentation
using one or multiple 2D images; and Geo AR, allowing for creation of
geo-markers at specific locations to triggered AR
content~\autocite{wikitude2018}.

@@

The company motive.io used to work on a product that would allow users to
create an engaging AR experience in the style of Pokémon Go. Their service
would have purportedly handled technical details such as hosting, storage, and
user accounts. The promotional video shows the creation of a location-based AR
game where the user pretends to hack into ATMs using the real-world locations
of ATMs in a city\autocite{odom2017}.

@@

In a question submitted to \textit{Compute!} magazine asking whether it is
possible for a Commodore 64 to emulate MS-DOS, the editor responded ``Yes, it's
possible for a 64 to emulate an IBM PC, in the same sense that it's possible to
bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
``Emulation is a complex business, but here's one rule of thumb: The only way to
successfully emulate a machine is with a much more powerful
machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
operating system is closer to emulating a C64 on an IBM PC running MS-DOS
(rather than the other way around, thankfully). The moral is that the speed
problem facing emulators is just as real as it was in 1988. Considering that AR
already pushes modern phone hardware to the limit, emulation is not something is
not something we wanted to struggle with. On top of this, our testing required
us to move the camera through the world at various speeds and angles, which is
simply cumbersome with a laptop webcam.

@@

The goal of Editour is to allow a non-technical user to design audio tours
through a web-app. At its core, Editour is a tool to draw arbitrarily-shaped
geographic regions onto a map.

@@

Even with knowledge of C\# and Unity, inputting tour data this way is obviously
not convenient. Atticus reminded us that, although he has a working knowledge
of Unity, he is not a software developer [citation needed for personal
communication.] In order to make our app prototype at all useful for the
future, we needed to provide an easy way to ``design'' a tour.

@@

\begin{minted}{json}
{
   "regions": [
      {
         "name": "Beautiful Place",
         "points": [ {"lat": 34.979222, "lng": 135.963628}, ... ],
         "audio": [ "beautiful-audio.mp3" ],
         "images": [ "mountain.jpg", "stream.jpg" ],
         "transcript": "To your left, you can see a beautiful place."
      },
      {
         "name": "Gorgeous Place",
         "points": [ {"lat": 34.979754, "lng": 135.964889}, ... ],
         "audio": [ "gorgeous-audio.mp3" ],
         "images": [ "hill.jpg", "valley.jpg", "gorge.jpg" ],
         "transcript", "To your right, you can see a gorgeous place."
      }
   ]
}
\end{minted}

@@

The backend implements a representational state transfer (REST) API.
In a ``RESTful'' service, web resources are manipulated with a predefined set of
stateless operations~\autocite{rfc7231}. Because the REST API is operated over
the Hypertext Transfer Protocol (HTTP), the available operations are just the
standard HTTP methods, such as GET, POST, and DELETE. For full documentation of
the backend's API, see Appendix~\ref{sec:editourAPIDocumentation}.

@@

Here is a list of API functions the Editour backend handles. The response is
usually a JSON like this with fields called \texttt{status} and \texttt{message}
The status is an HTTP status code like 200 (OK) or 404
(Not~Found)~\autocite{rfc7231}, and the message is a string or stringified JSON
that contains the data of the response.
